### 2017-07-26 Paper01_EnthalpyAndCrystallization.tex
DSC Film - added film DSC figures
Method - filed in XRD details

\subsection{\acrshort{xrd} characterization}
XRD heated in 5 degree increments at 20 k/min. scans of xx over a range of 30 - 60 2 theta allows 20 minute scans.

@@

@@

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.95\textwidth]{XRD_Annealing_Bulk.png}
	\caption[Table of contents Capition]{\acrshort{xrd} pattern for Bulk \MgZnCa~ heated through several crystallization peaks identified from \acrshort{dsc}}
	\label{fig:XRD_Annealing_Bulk}
\end{figure}

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.95\textwidth]{XRD_Annealing_Film.png}
	\caption[Table of contents Capition]{\acrshort{xrd} pattern for Film \MgZnCa~ heated through several crystallization peaks identified from \acrshort{dsc}}
	\label{fig:XRD_Annealing_Film}
\end{figure}

>>>>

\subsection{\acrshort{xrd} characterization}
Annealing XRD (PANalytical Empyrean) with a Cu $K_{\alpha}$ X-ray source ($\lambda = 1.541 \angstrom$ ). Generator Voltage 45, Tube Current 40, Scan Step Size 0.0262606, Time per step 397.29.

Dynamic XRD (Bruker D8) with a Cu $K_{\alpha}$ X-ray source ($\lambda = 1.541 \angstrom$ ). Generator Voltage 45, Tube Current 100, Scan Step Size 0.02, Time per step 134.4.

XRD heated in 5 degree increments at 20 k/min. scans of xx over a range of 31 - 60 2 theta allows 20 minute scans.

@@

%code to put 2 images side by side in a figure
\begin{figure}[b]
	\centering
	%Image 1
	\begin{subfigure}[htbp]{0.495\textwidth}
		\includegraphics[width=\textwidth]{DSC_Fragility_Film.png}
		\caption{}
		\label{fig:DSC_vHeatingRate_Film}
	\end{subfigure}
	%Image 2
	\begin{subfigure}[htbp]{0.495\textwidth}
		\includegraphics[width=\textwidth]{Onsets_BulkandFilm.png}
		\caption{}
		\label{fig:DSC_Onsets_Film}
	\end{subfigure}
	\caption{(a) Unrelaxed film \MgZnCa~ heated at various heating rates. The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx es of the $100 K/min$ sample. (b) The \Tg s and \Tx es of the bulk and film \MgZnCa~ at all heating rates. }%global caption
	\label{fig:DSC_Film}
\end{figure}

@@

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.9\textwidth]{XRD_Annealing_Bulk.png}
	\caption[Table of contents Capition]{\acrshort{xrd} pattern for Bulk \MgZnCa~ heated through several crystallization peaks identified from \acrshort{dsc}}
	\label{fig:XRD_Annealing_Bulk}
\end{figure}

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.9\textwidth]{XRD_Annealing_Film.png}
	\caption[Table of contents Capition]{\acrshort{xrd} pattern for Film \MgZnCa~ heated through several crystallization peaks identified from \acrshort{dsc}}
	\label{fig:XRD_Annealing_Film}
\end{figure}
